\documentclass[11pt,fleqn]{article}

%% This first part is the document header, which you don't need to edit.
%% Scroll down to \begin{document}

\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{mdframed}
\usepackage{color}

\setlength{\oddsidemargin}{0px}
\setlength{\textwidth}{460px}
\setlength{\voffset}{-1.5cm}
\setlength{\textheight}{20cm}
\setlength{\parindent}{0px}
\setlength{\parskip}{10pt}
\begin{document}

\title{Introduction to \bf{Java}}
\author{Tim Magoun and Aravind Koneru}
\date{\it{compiled on} \today}
\maketitle

\pagenumbering{arabic}

This test will evaluate the familiarity of basic programming concepts as well as the knowledge of the
Java programming language, which is used as the programming language of numerous FIRST\textsuperscript\textregistered
robotics competitions.


\vspace{5mm}
The following topics will be on this test:
\begin{itemize}
\item Primitive Types and Operations (\textit{int, byte, boolean, etc.})
\item Modifiers (\textit{final, public, static, etc.})*
\item Comparison Operators (\textit{==, !=, $\mathit{>}$=,etc.})
\item Assignment operators (\textit{+=, *=, =, etc})
\item Flow Control (\textit{if, for, break, etc})
\item Methods and Parameters*
\item Single- and Multi-Dimensional Arrays
\item Object Oriented Programming*
\item Inheritance and Polymorphism*
\item Programming Habits and Conventions
\end{itemize}

* Starred items are extremely important in programming a robot
\vfill
\begin{center}
\textbf{DO NOT BEGIN UNTIL INSTRUCTED TO DO SO}
\end{center}
\newpage

\begin{center}
\begin{large}
PART ONE: Multiple Choice
\end{large}
\end{center}
\textit{Instructions: Choose the correct solution to the problem, there is only one correct answer for each problem.}

\begin{enumerate}
\item Example Question One
	\begin{enumerate}
	\item Answer One
	\item Answer Two
	\item Answer Three
	\item Answer Four
	\end{enumerate}
\item Example Question Two
	\begin{enumerate}
	\item Answer One
	\item Answer Two
	\item Answer Three
	\item Answer Four
	\end{enumerate}
\end{enumerate}

\vfill
\begin{center}
\textbf{CONTINUE TO THE NEXT PAGE}
\end{center}

\newpage

\begin{center}
\begin{large}
PART TWO: Open Ended Response
\end{large}
\end{center}
\textit{Instructions: Write the most efficient solution to the following methods. You will \textbf{not} be given any extra paper.}

\begin{enumerate}
\item Write a method that will return an array of $n$ length, filled with the decimal approximations of the sequence $\left[ \frac{1}{1}, \frac{1}{2}, \frac{1}{3}, \frac{1}{4}, \cdots, \frac{1}{n} \right]$ where $n$ is the integer parameter of the method.
\vfill
\begin{center}
\textbf{DO NOT CONTINUE UNTIL INSTRUCTED TO DO SO}
\end{center}
\newpage
\item Write a method that will recursively determine if a word \emph{str} is a palindrome, where \emph{str} is a string parameter of the method.
\vfill
\begin{center}
\textbf{END OF EXAM}
\end{center}
\end{enumerate}


\end{document}