\documentclass[11pt,fleqn]{article}

%% This first part is the document header, which you don't need to edit.
%% Scroll down to \begin{document}

\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{mdframed}
\usepackage{minted}
\usepackage{color}
\usepackage{datetime}
\usepackage{graphicx}
%%Please place all images used in documents in the images folder
\graphicspath{ {../images/} }

\setlength{\oddsidemargin}{0px}
\setlength{\textwidth}{460px}
\setlength{\voffset}{-1.5cm}
\setlength{\textheight}{20cm}
\setlength{\parindent}{0px}
\setlength{\parskip}{10pt}

\newcommand{\mil}[2][java]{\mintinline{#1}|#2|}
%% This command allows quick use of \mintinline feature, default language is java.

%% USAGE: \mil (optional)[<language>] {content}

%% EXAMPLE: \mil[python]{if not x == 3}
%% 			\mil{if (x.equals(y)}

\begin{document}
\title{Problem Set 4}%Insert Title here
\author{Tim Magoun and Aravind Koneru}
\date{\textit{Compiled on} \today \hspace{1mm} at \currenttime}
\maketitle

\begin{center}
\textbf{Do these problems for additional practice and challenge}
\end{center}

Reminders:
\begin{itemize}
    \item
        Make sure that problem 2 and 3 are both methods

    \item
        Submit these problems to Dr. Rogers no later than Tuesday, August 2 by 9:00 am

    \item
        Email the .java files as we discussed in class instead of copying the code into the email

    \item
        If you don't solve every problem, it's fine. Just send us what you did. That being said,
        please refrain from copying the answers from online. All the instructors are aware that many
        of the problems that we give you can be found on StackOverflow and other community sites AND
        we do notice when a solution has been plagiarized. 

    \item
        There is no challenge question this week. Instead, prioritize doing as much of problem 1 as
        you can before moving onto problems 2 and 3. 
\end{itemize}

\begin{enumerate}
    \item
        \textbf{Date}: This problem will take the majority of your time this week. All the details
        are in the code as comments. Try to complete as many of the methods as you can. 

        \inputminted{java}{../../src/ps_4/Date.java}

    \item
        \textbf{isPrime(int x)}: We did this problem a few weeks ago, but now convert it into a method that
        accepts an \texttt{int} and returns a \texttt{boolean}. For example, I should be able to
        call \texttt{isPrime(3)} and it would return \texttt{true}. 

    \item
        \textbf{printPrimes(int x)}: This method should print out the first \textit{x} many primes. 
        For example, I should be able to call \texttt{printPrimes(5)} and it would print out the first 5 
        prime numbers. 

        Hint: Consider using the \texttt{isPrime} method to solve this problem. 
\end{enumerate}

\end{document}
